Scaling Automated Theory Exploration

### 2015-08-06 AI4FM/abstract.tex
Use template

\documentclass[]{eceasst}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
    \usepackage{xltxtra,xunicode}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
% \ifxetex
%   \usepackage[setpagesize=false, % page size defined by xetex
%               unicode=false, % unicode breaks when used with xetex
%               xetex]{hyperref}
% \else
%   \usepackage[unicode=true]{hyperref}
% \fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={Chris Warburton},
            pdftitle={Scaling Automated Theory Exploration},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}

\title{Scaling Automated Theory Exploration}
\author{Chris Warburton}
\date{}
\usepackage[T1]{fontenc}
\usepackage{upquote}

% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

\begin{abstract}

In this paper we investigate the \textbf{theory exploration} (TE)
paradigm for computer-assisted Mathematics and identify limitations and
improvements of current approaches. Unlike the theorem-proving paradigm,
which requires user-provided conjectures, TE performs an open-ended
search for theorems satisfying given criteria. We see promise in TE for
identifying new abstractions and connections in libraries of software
and proofs, but realising this potential requires more scalable
algorithms than presently used.

\end{abstract}

\section{Introduction}\label{introduction}

@@

\section{Tackling Complexity}\label{tackling-complexity}

@@

\section{Existing Work}\label{existing-work}

@@

\section{Going Forward}\label{going-forward}

@@

\section{Acknowlegements}\label{acknowlegements}

I am grateful for those who have helped formulate these ideas through
conversation, especially the HipSpec team at Chalmers University (Moa
Johansson, Koen Claessen, Nick Smallbone and Dan Rosén) and my
supervisor Katya Komendantskaya. I also wish to thank the implementors
of the systems we are building on, including HipSpec, QuickSpec and
QuickCheck on the theory exploration side, as well as GHC, Cabal and Nix
on the infrastructure side.

\bibliographystyle{plain} \bibliography{../Bibtex}

>>>>

\documentclass{eceasst}
% This is an empty ECEASST article that can be used as a template
% by authors.
% Just uncomment the appropriate frontmatter commands and provide
% the parameters.

% Required packages
% =================
% Your \usepackage commands go here.

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

% Volume frontmatter
% ==================
\input{frontmatter}

% Article frontmatter
% ===================
\title{Scaling Automated Theory Exploration} % Title of the article
%\short{} % Short title of the article (optional)
\author{Chris Warburton\sponsor{}} % Authors and references to addresses
\institute{ % Institutes with labels
\email{cmwarburton@dundee.ac.uk}, \url{http://www.computing.dundee.ac.uk/about/staff/124}\\
School of Computing\\
University of Dundee}
\abstract{
We investigate the \textbf{theory exploration} (TE)
paradigm for computer-assisted Mathematics and identify limitations and
improvements for current approaches. Unlike the theorem-proving paradigm,
which requires user-provided conjectures, TE performs an open-ended
search for theorems satisfying given criteria. We see promise in TE for
identifying new abstractions and connections in libraries of software
and proofs, but realising this potential requires more scalable
algorithms than presently used.} % Abstract of the article
%\keywords{} % Keywords for the article

@@

% Main part of your article
% =========================
\section{Introduction}

@@

\section{Tackling Complexity}

@@

\section{Existing Work}

@@

\section{Going Forward}

@@

% Acknowledgements for colleagues, referees, ...
% ==============================================
\begin{acknowledge}
I am grateful for those who have helped formulate these ideas through
conversation, especially the HipSpec team at Chalmers University (Moa
Johansson, Koen Claessen, Nick Smallbone, Dan Rosén and Irene Lobo Valbuena)
and my supervisor Katya Komendantskaya. I also wish to thank the implementors
of the systems we are building on, including HipSpec, QuickSpec and
QuickCheck on the theory exploration side, as well as GHC, Cabal and Nix
on the infrastructure side.
\end{acknowledge}

% Bibliography with BibTeX
% ========================
\bibliographystyle{eceasst}
\bibliography{../Bibtex}
